Polynomial expansions of finite volume data in a cut cell context

### 2023-04-25 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
further refinements on the document.   EBCM framework coming out the cold.

To gain insight into the connection between solvability, weighting and
order, we evaluate the matrix $A \equiv (WM)^T(WM)$
at every volume in a computational grid and analyze its
eigenvalues.   Given a matrix $A_i$ with the set of eigenvalues
$\{ \lambda_{i}\}$, the inverse of the condition number $I_i$ is given by
\begin{equation*}
  I_i = \frac{\lambda_i|_{min}}{\lambda_i|_{max}},
\end{equation*}
which goes to zero as the maximum and minimum eigenvalues diverge and
the matrix becomes more poorly conditioned.   These eigenvalues are
obtained through  SVD decompostion \footnotemark[7].

@@

\begin{small}
\begin{table}
\begin{center}
\begin{tabular}{|cccc|ccc|} \hline
$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
\hline
2 & 1 & 1 & 3 & 2.280975e+00 & 1.471897e-03 & 6.452929e-04 \\ 
2 & 1 & 2 & 3 & 1.184453e+00 & 1.544110e-04 & 1.303648e-04 \\ 
2 & 1 & 3 & 3 & 1.036586e+00 & 2.327227e-05 & 2.245088e-05 \\ 
2 & 1 & 4 & 3 & 1.008340e+00 & 4.569664e-06 & 4.531869e-06 \\ 
2 & 1 & 5 & 3 & 1.002008e+00 & 1.029556e-06 & 1.027493e-06 \\ 
2 & 2 & 1 & 3 & 2.280983e+00 & 1.185321e-06 & 5.196535e-07 \\ 
2 & 2 & 2 & 3 & 1.184453e+00 & 8.194451e-08 & 6.918341e-08 \\ 
2 & 2 & 3 & 3 & 1.036586e+00 & 5.067663e-09 & 4.888801e-09 \\ 
2 & 2 & 4 & 3 & 1.008340e+00 & 3.385548e-10 & 3.357547e-10 \\ 
2 & 2 & 5 & 3 & 1.002008e+00 & 2.634337e-11 & 2.629058e-11 \\ 
2 & 3 & 1 & 3 & 2.280983e+00 & 5.060791e-10 & 2.218689e-10 \\ 
2 & 3 & 2 & 3 & 1.184453e+00 & 4.179917e-11 & 3.528985e-11 \\ 
2 & 3 & 3 & 3 & 1.036586e+00 & 2.762010e-12 & 2.664525e-12 \\ 
2 & 3 & 4 & 3 & 1.008340e+00 & 1.380647e-13 & 1.369228e-13 \\ 
2 & 3 & 5 & 3 & 1.002008e+00 & 6.886907e-15 & 6.873105e-15 \\ 
2 & 4 & 1 & 3 & 2.744326e+00 & 2.848432e-25 & 1.037935e-25 \\ 
2 & 4 & 2 & 3 & 1.184453e+00 & 1.481174e-27 & 1.250513e-27 \\ 
2 & 4 & 3 & 3 & 1.055930e+00 & 4.257688e-26 & 4.032168e-26 \\ 
2 & 4 & 4 & 3 & 1.008340e+00 & 1.078564e-23 & 1.069643e-23 \\ 
2 & 4 & 5 & 3 & 1.002008e+00 & 5.873348e-25 & 5.861578e-25 \\ 
3 & 1 & 1 & 3 & 4.207341e+00 & 3.347096e-03 & 7.955372e-04 \\ 
3 & 1 & 2 & 3 & 1.335375e+00 & 2.299835e-04 & 1.722239e-04 \\ 
3 & 1 & 3 & 3 & 1.058688e+00 & 2.726319e-05 & 2.575186e-05 \\ 
3 & 1 & 4 & 3 & 1.012826e+00 & 4.843834e-06 & 4.782494e-06 \\ 
3 & 1 & 5 & 3 & 1.003042e+00 & 1.052599e-06 & 1.049406e-06 \\ 
3 & 2 & 1 & 3 & 4.207383e+00 & 2.698941e-06 & 6.414775e-07 \\ 
3 & 2 & 2 & 3 & 1.335376e+00 & 1.349331e-07 & 1.010450e-07 \\ 
3 & 2 & 3 & 3 & 1.058688e+00 & 6.504992e-09 & 6.144388e-09 \\ 
3 & 2 & 4 & 3 & 1.012826e+00 & 3.782273e-10 & 3.734376e-10 \\ 
3 & 2 & 5 & 3 & 1.003042e+00 & 2.753365e-11 & 2.745014e-11 \\ 
3 & 3 & 1 & 3 & 4.207383e+00 & 1.150489e-09 & 2.734453e-10 \\ 
3 & 3 & 2 & 3 & 1.335376e+00 & 6.641096e-11 & 4.973204e-11 \\ 
3 & 3 & 3 & 3 & 1.058688e+00 & 3.224905e-12 & 3.046133e-12 \\ 
3 & 3 & 4 & 3 & 1.012826e+00 & 1.004670e-13 & 9.919476e-14 \\ 
3 & 3 & 5 & 3 & 1.003042e+00 & 3.476637e-15 & 3.466092e-15 \\ 
3 & 4 & 1 & 3 & 5.166875e+00 & 1.524000e-25 & 2.949559e-26 \\ 
3 & 4 & 2 & 3 & 1.474014e+00 & 1.231139e-27 & 8.352288e-28 \\ 
3 & 4 & 3 & 3 & 1.102368e+00 & 5.433012e-27 & 4.928491e-27 \\ 
3 & 4 & 4 & 3 & 1.012826e+00 & 1.327379e-23 & 1.310570e-23 \\ 
3 & 4 & 5 & 3 & 1.003042e+00 & 6.807789e-25 & 6.787141e-25 \\
\hline
\end{tabular}
\end{center}
\label{tab::worst_all_reg_inv_conv}
\caption
    {
      We show the lowest value of
      $I$ for an entire Cartesian grid of size $32^D$.
      We vary Taylor power $P^T$, weighting
      function exponents $P^W$, and dimensionality $D$. 
    }
\end{table}
\end{small}

@@

\begin{small}
\begin{table}
\begin{center}
\begin{tabular}{|cccc|ccc|} \hline
$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
  \hline
2 & 1 & 1 & 3 & 2.652364e+00 & 1.404997e-03 & 5.297151e-04 \\ 
2 & 1 & 2 & 3 & 1.208056e+00 & 1.014262e-04 & 8.395817e-05 \\ 
2 & 1 & 3 & 3 & 1.038877e+00 & 8.361926e-06 & 8.049002e-06 \\ 
2 & 1 & 4 & 3 & 1.008924e+00 & 1.034928e-06 & 1.025774e-06 \\ 
2 & 1 & 5 & 3 & 1.002428e+00 & 1.818655e-07 & 1.814249e-07 \\ 
2 & 2 & 1 & 3 & 2.714706e+00 & 6.503682e-07 & 2.395722e-07 \\ 
2 & 2 & 2 & 3 & 1.208056e+00 & 4.514952e-08 & 3.737369e-08 \\ 
2 & 2 & 3 & 3 & 1.038878e+00 & 2.933277e-09 & 2.823506e-09 \\ 
2 & 2 & 4 & 3 & 1.008924e+00 & 1.838097e-10 & 1.821840e-10 \\ 
2 & 2 & 5 & 3 & 1.002428e+00 & 1.202042e-11 & 1.199130e-11 \\ 
2 & 3 & 1 & 3 & 2.714706e+00 & 2.057098e-10 & 7.577609e-11 \\ 
2 & 3 & 2 & 3 & 1.208056e+00 & 1.761011e-11 & 1.457723e-11 \\ 
2 & 3 & 3 & 3 & 1.039039e+00 & 1.175442e-12 & 1.131278e-12 \\ 
2 & 3 & 4 & 3 & 1.008867e+00 & 6.513002e-14 & 6.455759e-14 \\ 
2 & 3 & 5 & 3 & 1.002428e+00 & 3.467198e-15 & 3.458798e-15 \\ 
2 & 4 & 1 & 3 & 2.714706e+00 & 1.027685e-15 & 3.785620e-16 \\   
2 & 4 & 2 & 3 & 1.211905e+00 & 6.107792e-17 & 5.039827e-17 \\ 
2 & 4 & 3 & 3 & 1.056037e+00 & 5.698627e-18 & 5.396236e-18 \\ 
2 & 4 & 4 & 3 & 1.012707e+00 & 1.518532e-18 & 1.499478e-18 \\ 
2 & 4 & 5 & 3 & 1.003135e+00 & 5.995871e-19 & 5.977134e-19 \\ 
3 & 1 & 1 & 3 & 6.913890e+00 & 3.982271e-03 & 5.759812e-04 \\ 
3 & 1 & 2 & 3 & 1.457799e+00 & 1.829378e-04 & 1.254890e-04 \\ 
3 & 1 & 3 & 3 & 1.066961e+00 & 8.913398e-06 & 8.354003e-06 \\ 
3 & 1 & 4 & 3 & 1.014131e+00 & 7.252280e-07 & 7.151226e-07 \\ 
3 & 1 & 5 & 3 & 1.003774e+00 & 1.047053e-07 & 1.043116e-07 \\ 
3 & 2 & 1 & 3 & 7.173851e+00 & 1.868373e-06 & 2.604421e-07 \\ 
3 & 2 & 2 & 3 & 1.457801e+00 & 7.350629e-08 & 5.042274e-08 \\ 
3 & 2 & 3 & 3 & 1.066958e+00 & 3.054784e-09 & 2.863077e-09 \\ 
3 & 2 & 4 & 3 & 1.014128e+00 & 1.439525e-10 & 1.419470e-10 \\ 
3 & 2 & 5 & 3 & 1.003771e+00 & 6.965181e-12 & 6.939012e-12 \\ 
3 & 3 & 1 & 3 & 7.173852e+00 & 5.736142e-10 & 7.995902e-11 \\ 
3 & 3 & 2 & 3 & 1.463399e+00 & 3.367341e-11 & 2.301041e-11 \\ 
3 & 3 & 3 & 3 & 1.067176e+00 & 1.250758e-12 & 1.172027e-12 \\ 
3 & 3 & 4 & 3 & 1.014128e+00 & 4.489644e-14 & 4.427098e-14 \\ 
3 & 3 & 5 & 3 & 1.003771e+00 & 1.609961e-15 & 1.603912e-15 \\ 
3 & 4 & 1 & 3 & 7.173852e+00 & 8.922302e-15 & 1.243725e-15 \\ 
3 & 4 & 2 & 3 & 1.463399e+00 & 3.078368e-16 & 2.103574e-16 \\ 
3 & 4 & 3 & 3 & 1.067186e+00 & 2.577668e-17 & 2.415387e-17 \\ 
3 & 4 & 4 & 3 & 1.014048e+00 & 4.440651e-18 & 4.379133e-18 \\ 
3 & 4 & 5 & 3 & 1.005227e+00 & 8.527341e-19 & 8.483000e-19 \\
\hline
\end{tabular}
\end{center}
\label{tab::worst_unmerged_inv_conv}
\caption
    {
      We show the lowest value of
      $I$ for an entire Cartesian grid of size $32^D$.
      Volumes are  formed by a sphere (or circle in 2D) cutting the
      grid.   Volumes here can be arbitrarily small (no cell merging
      happens here).
      We vary Taylor power $P^T$, weighting
      function exponents $P^W$, and dimensionality $D$. 
    }
\end{table}
\end{small}

\begin{table}
\begin{center}
\begin{tabular}{|cccc|ccc|} \hline
$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
  \hline
2 & 1 & 1 & 3 & 2.516834e+00 & 1.345987e-04 & 5.347936e-05 \\ 
2 & 1 & 2 & 3 & 1.940391e+00 & 5.761694e-06 & 2.969347e-06 \\ 
2 & 1 & 3 & 3 & 1.890620e+00 & 3.134007e-07 & 1.657661e-07 \\ 
2 & 1 & 4 & 3 & 2.315204e+00 & 2.362198e-08 & 1.020298e-08 \\ 
2 & 1 & 5 & 3 & 2.314798e+00 & 1.256411e-09 & 5.427736e-10 \\ 
2 & 2 & 1 & 3 & 5.133178e+00 & 3.150951e-08 & 6.138402e-09 \\ 
2 & 2 & 2 & 3 & 3.875948e+00 & 1.019905e-09 & 2.631369e-10 \\ 
2 & 2 & 3 & 3 & 3.677407e+00 & 3.374831e-11 & 9.177202e-12 \\ 
2 & 2 & 4 & 3 & 3.633887e+00 & 1.196563e-12 & 3.292791e-13 \\ 
2 & 2 & 5 & 3 & 1.100852e+00 & 1.071019e-14 & 9.729001e-15 \\ 
2 & 3 & 1 & 3 & 1.461766e+00 & 8.698889e-14 & 5.950944e-14 \\ 
2 & 3 & 2 & 3 & 1.118751e+00 & 4.096970e-15 & 3.662093e-15 \\ 
2 & 3 & 3 & 3 & 1.102424e+00 & 1.662951e-16 & 1.508449e-16 \\ 
2 & 3 & 4 & 3 & 3.178329e+00 & 1.221190e-16 & 3.842238e-17 \\ 
2 & 3 & 5 & 3 & 1.924223e+00 & 3.044738e-18 & 1.582320e-18 \\ 
3 & 1 & 1 & 3 & 5.278376e+00 & 5.346601e-04 & 1.012926e-04 \\ 
3 & 1 & 2 & 3 & 2.898394e+00 & 1.760686e-05 & 6.074697e-06 \\ 
3 & 1 & 3 & 3 & 2.480330e+00 & 4.867477e-07 & 1.962431e-07 \\ 
3 & 1 & 4 & 3 & 2.602304e+00 & 1.708061e-08 & 6.563648e-09 \\ 
3 & 1 & 5 & 3 & 2.594257e+00 & 5.017396e-10 & 1.934039e-10 \\ 
3 & 2 & 1 & 3 & 8.172169e+00 & 1.320095e-07 & 1.615355e-08 \\ 
3 & 2 & 2 & 3 & 4.770044e+00 & 3.005370e-09 & 6.300508e-10 \\ 
3 & 2 & 3 & 3 & 4.426838e+00 & 7.734334e-11 & 1.747146e-11 \\ 
3 & 2 & 4 & 3 & 4.521378e+00 & 1.996373e-12 & 4.415410e-13 \\ 
3 & 2 & 5 & 3 & 4.508090e+00 & 4.439516e-14 & 9.847886e-15 \\ 
3 & 3 & 1 & 3 & 5.015663e+00 & 9.627815e-12 & 1.919550e-12 \\ 
3 & 3 & 2 & 3 & 6.602139e+00 & 4.969235e-13 & 7.526705e-14 \\ 
3 & 3 & 3 & 3 & 6.132610e+00 & 1.126536e-14 & 1.836961e-15 \\ 
3 & 3 & 4 & 3 & 5.482751e+00 & 3.670736e-16 & 6.695062e-17 \\ 
3 & 3 & 5 & 3 & 5.346895e+00 & 4.774068e-17 & 8.928674e-18 \\ 
3 & 4 & 1 & 3 & 1.161979e+01 & 5.372252e-18 & 4.623365e-19 \\ 
3 & 4 & 2 & 3 & 4.069086e+00 & 1.622222e-17 & 3.986699e-18 \\
\hline
\end{tabular}
\end{center}
\label{tab::worst_merged_inv_conv}
\caption
    {
      We show the lowest value of
      $I$ for an entire Cartesian grid of size $32^D$.
      Volumes are  formed by a sphere (or circle in 2D) cutting the
      grid.   Small volumes here are merged with neighbors.
      We vary Taylor power $P^T$, weighting
      function exponents $P^W$, and dimensionality $D$. 
    }
\end{table}

@@

We do also show that matrix conditioning is a  potential issue for
this class of algorihms.   In fact, for certain parameters,
the condition number  can be so severe that an
increase in matrix arithmetic precision will not be sufficient.
Since cell merger does not really help the
problem, this lack of conditioning is not an issue with small cells.
With careful choices of polynomial order and weighting matrix, the
solvability problem can be managed, however.

>>>>

To gain insight into the connection between solvability, weighting and
order, we evaluate the matrix
\begin{equation}
A \equiv (WM)^T(WM)
\label{eqn::normalEq}
\end{equation}
at every volume in a computational grid and analyze its
eigenvalues.   Given a matrix $A_i$ with the set of eigenvalues
$\{ \lambda_{i}\}$, the inverse of the condition number $I_i$ is given by
\begin{equation*}
  I_i = \frac{\lambda_i|_{min}}{\lambda_i|_{max}},
\end{equation*}
which goes to zero as the maximum and minimum eigenvalues diverge and
the matrix becomes more poorly conditioned.   These eigenvalues are
obtained through  SVD decompostion \footnotemark[7].

Solving the normal equations (\ref{eqn::normalEq}) for the
coeffients is not ideal because the condition number of $A$ is the
square of the condition number of
$WM$  \cite{BigCheese}.     SVD can be used to solve the system with
the condition number of $WM$.   That, however, requires interweaving
the computation of the stencil with  the target application's
equations.   Since we are doing this 
analysis in the absence of a
specific target stancil, one should interpret our condition number
results as the square of the effective condition number that algorithm
developers will encounter.

@@

\begin{small}
\begin{table}
\begin{center}
\begin{tabular}{|cccc|ccc|} \hline
$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
\hline
2 & 1 & 1 & 3 & 2.280975e+00 & 1.471897e-03 & 6.452929e-04 \\ 
2 & 1 & 2 & 3 & 1.184453e+00 & 1.544110e-04 & 1.303648e-04 \\ 
2 & 1 & 3 & 3 & 1.036586e+00 & 2.327227e-05 & 2.245088e-05 \\ 
2 & 1 & 4 & 3 & 1.008340e+00 & 4.569664e-06 & 4.531869e-06 \\ 
2 & 1 & 5 & 3 & 1.002008e+00 & 1.029556e-06 & 1.027493e-06 \\
\hline
2 & 2 & 1 & 3 & 2.280983e+00 & 1.185321e-06 & 5.196535e-07 \\ 
2 & 2 & 2 & 3 & 1.184453e+00 & 8.194451e-08 & 6.918341e-08 \\ 
2 & 2 & 3 & 3 & 1.036586e+00 & 5.067663e-09 & 4.888801e-09 \\ 
2 & 2 & 4 & 3 & 1.008340e+00 & 3.385548e-10 & 3.357547e-10 \\ 
2 & 2 & 5 & 3 & 1.002008e+00 & 2.634337e-11 & 2.629058e-11 \\ 
\hline
2 & 3 & 1 & 3 & 2.280983e+00 & 5.060791e-10 & 2.218689e-10 \\ 
2 & 3 & 2 & 3 & 1.184453e+00 & 4.179917e-11 & 3.528985e-11 \\ 
2 & 3 & 3 & 3 & 1.036586e+00 & 2.762010e-12 & 2.664525e-12 \\ 
2 & 3 & 4 & 3 & 1.008340e+00 & 1.380647e-13 & 1.369228e-13 \\ 
2 & 3 & 5 & 3 & 1.002008e+00 & 6.886907e-15 & 6.873105e-15 \\ 
\hline
2 & 4 & 1 & 3 & 2.744326e+00 & 2.848432e-25 & 1.037935e-25 \\ 
2 & 4 & 2 & 3 & 1.184453e+00 & 1.481174e-27 & 1.250513e-27 \\ 
2 & 4 & 3 & 3 & 1.055930e+00 & 4.257688e-26 & 4.032168e-26 \\ 
2 & 4 & 4 & 3 & 1.008340e+00 & 1.078564e-23 & 1.069643e-23 \\ 
2 & 4 & 5 & 3 & 1.002008e+00 & 5.873348e-25 & 5.861578e-25 \\ 
\hline
3 & 1 & 1 & 3 & 4.207341e+00 & 3.347096e-03 & 7.955372e-04 \\ 
3 & 1 & 2 & 3 & 1.335375e+00 & 2.299835e-04 & 1.722239e-04 \\ 
3 & 1 & 3 & 3 & 1.058688e+00 & 2.726319e-05 & 2.575186e-05 \\ 
3 & 1 & 4 & 3 & 1.012826e+00 & 4.843834e-06 & 4.782494e-06 \\ 
3 & 1 & 5 & 3 & 1.003042e+00 & 1.052599e-06 & 1.049406e-06 \\ 
\hline
3 & 2 & 1 & 3 & 4.207383e+00 & 2.698941e-06 & 6.414775e-07 \\ 
3 & 2 & 2 & 3 & 1.335376e+00 & 1.349331e-07 & 1.010450e-07 \\ 
3 & 2 & 3 & 3 & 1.058688e+00 & 6.504992e-09 & 6.144388e-09 \\ 
3 & 2 & 4 & 3 & 1.012826e+00 & 3.782273e-10 & 3.734376e-10 \\ 
3 & 2 & 5 & 3 & 1.003042e+00 & 2.753365e-11 & 2.745014e-11 \\ 
\hline
3 & 3 & 1 & 3 & 4.207383e+00 & 1.150489e-09 & 2.734453e-10 \\ 
3 & 3 & 2 & 3 & 1.335376e+00 & 6.641096e-11 & 4.973204e-11 \\ 
3 & 3 & 3 & 3 & 1.058688e+00 & 3.224905e-12 & 3.046133e-12 \\ 
3 & 3 & 4 & 3 & 1.012826e+00 & 1.004670e-13 & 9.919476e-14 \\ 
3 & 3 & 5 & 3 & 1.003042e+00 & 3.476637e-15 & 3.466092e-15 \\ 
\hline
3 & 4 & 1 & 3 & 5.166875e+00 & 1.524000e-25 & 2.949559e-26 \\ 
3 & 4 & 2 & 3 & 1.474014e+00 & 1.231139e-27 & 8.352288e-28 \\ 
3 & 4 & 3 & 3 & 1.102368e+00 & 5.433012e-27 & 4.928491e-27 \\ 
3 & 4 & 4 & 3 & 1.012826e+00 & 1.327379e-23 & 1.310570e-23 \\ 
3 & 4 & 5 & 3 & 1.003042e+00 & 6.807789e-25 & 6.787141e-25 \\
\hline
\end{tabular}
\end{center}
\label{tab::worst_all_reg_inv_conv}
\caption
    {
      We show the lowest value of
      $I$ for an entire Cartesian grid of size $32^D$.
      We vary Taylor power $P^T$, weighting
      function exponents $P^W$, and dimensionality $D$.   Keep in mind
      that the effective condition number of the problem will be $(1/\sqrt(I))$.
    }
\end{table}
\end{small}

@@

\begin{small}
\begin{table}
\begin{center}
\begin{tabular}{|cccc|ccc|} \hline
$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
  \hline
2 & 1 & 1 & 3 & 2.652364e+00 & 1.404997e-03 & 5.297151e-04 \\ 
2 & 1 & 2 & 3 & 1.208056e+00 & 1.014262e-04 & 8.395817e-05 \\ 
2 & 1 & 3 & 3 & 1.038877e+00 & 8.361926e-06 & 8.049002e-06 \\ 
2 & 1 & 4 & 3 & 1.008924e+00 & 1.034928e-06 & 1.025774e-06 \\ 
2 & 1 & 5 & 3 & 1.002428e+00 & 1.818655e-07 & 1.814249e-07 \\
\hline
2 & 2 & 1 & 3 & 2.714706e+00 & 6.503682e-07 & 2.395722e-07 \\ 
2 & 2 & 2 & 3 & 1.208056e+00 & 4.514952e-08 & 3.737369e-08 \\ 
2 & 2 & 3 & 3 & 1.038878e+00 & 2.933277e-09 & 2.823506e-09 \\ 
2 & 2 & 4 & 3 & 1.008924e+00 & 1.838097e-10 & 1.821840e-10 \\ 
2 & 2 & 5 & 3 & 1.002428e+00 & 1.202042e-11 & 1.199130e-11 \\ 
\hline
2 & 3 & 1 & 3 & 2.714706e+00 & 2.057098e-10 & 7.577609e-11 \\ 
2 & 3 & 2 & 3 & 1.208056e+00 & 1.761011e-11 & 1.457723e-11 \\ 
2 & 3 & 3 & 3 & 1.039039e+00 & 1.175442e-12 & 1.131278e-12 \\ 
2 & 3 & 4 & 3 & 1.008867e+00 & 6.513002e-14 & 6.455759e-14 \\ 
2 & 3 & 5 & 3 & 1.002428e+00 & 3.467198e-15 & 3.458798e-15 \\ 
\hline
2 & 4 & 1 & 3 & 2.714706e+00 & 1.027685e-15 & 3.785620e-16 \\   
2 & 4 & 2 & 3 & 1.211905e+00 & 6.107792e-17 & 5.039827e-17 \\ 
2 & 4 & 3 & 3 & 1.056037e+00 & 5.698627e-18 & 5.396236e-18 \\ 
2 & 4 & 4 & 3 & 1.012707e+00 & 1.518532e-18 & 1.499478e-18 \\ 
2 & 4 & 5 & 3 & 1.003135e+00 & 5.995871e-19 & 5.977134e-19 \\ 
\hline
3 & 1 & 1 & 3 & 6.913890e+00 & 3.982271e-03 & 5.759812e-04 \\ 
3 & 1 & 2 & 3 & 1.457799e+00 & 1.829378e-04 & 1.254890e-04 \\ 
3 & 1 & 3 & 3 & 1.066961e+00 & 8.913398e-06 & 8.354003e-06 \\ 
3 & 1 & 4 & 3 & 1.014131e+00 & 7.252280e-07 & 7.151226e-07 \\ 
3 & 1 & 5 & 3 & 1.003774e+00 & 1.047053e-07 & 1.043116e-07 \\ 
\hline
3 & 2 & 1 & 3 & 7.173851e+00 & 1.868373e-06 & 2.604421e-07 \\ 
3 & 2 & 2 & 3 & 1.457801e+00 & 7.350629e-08 & 5.042274e-08 \\ 
3 & 2 & 3 & 3 & 1.066958e+00 & 3.054784e-09 & 2.863077e-09 \\ 
3 & 2 & 4 & 3 & 1.014128e+00 & 1.439525e-10 & 1.419470e-10 \\ 
3 & 2 & 5 & 3 & 1.003771e+00 & 6.965181e-12 & 6.939012e-12 \\ 
\hline
3 & 3 & 1 & 3 & 7.173852e+00 & 5.736142e-10 & 7.995902e-11 \\ 
3 & 3 & 2 & 3 & 1.463399e+00 & 3.367341e-11 & 2.301041e-11 \\ 
3 & 3 & 3 & 3 & 1.067176e+00 & 1.250758e-12 & 1.172027e-12 \\ 
3 & 3 & 4 & 3 & 1.014128e+00 & 4.489644e-14 & 4.427098e-14 \\ 
3 & 3 & 5 & 3 & 1.003771e+00 & 1.609961e-15 & 1.603912e-15 \\ 
\hline
3 & 4 & 1 & 3 & 7.173852e+00 & 8.922302e-15 & 1.243725e-15 \\ 
3 & 4 & 2 & 3 & 1.463399e+00 & 3.078368e-16 & 2.103574e-16 \\ 
3 & 4 & 3 & 3 & 1.067186e+00 & 2.577668e-17 & 2.415387e-17 \\ 
3 & 4 & 4 & 3 & 1.014048e+00 & 4.440651e-18 & 4.379133e-18 \\ 
3 & 4 & 5 & 3 & 1.005227e+00 & 8.527341e-19 & 8.483000e-19 \\
\hline
\end{tabular}
\end{center}
\label{tab::worst_unmerged_inv_conv}
\caption
    {
      We show the lowest value of
      $I$ for an entire Cartesian grid of size $32^D$.
      Volumes are  formed by a sphere (or circle in 2D) cutting the
      grid.   Volumes here can be arbitrarily small (no cell merging
      happens here).
      We vary Taylor power $P^T$, weighting
      function exponents $P^W$, and dimensionality $D$. 
      Keep in mind
      that the effective condition number of the problem will be $(1/\sqrt(I))$.
    }
\end{table}
\end{small}

\begin{table}
\begin{center}
\begin{tabular}{|cccc|ccc|} \hline
$D$ & $P^T$  & $P^W$ & $R_s$ & $\lambda_{max}$ & $\lambda_{min}$   & $I$ \\
  \hline
2 & 1 & 1 & 3 & 2.516834e+00 & 1.345987e-04 & 5.347936e-05 \\ 
2 & 1 & 2 & 3 & 1.940391e+00 & 5.761694e-06 & 2.969347e-06 \\ 
2 & 1 & 3 & 3 & 1.890620e+00 & 3.134007e-07 & 1.657661e-07 \\ 
2 & 1 & 4 & 3 & 2.315204e+00 & 2.362198e-08 & 1.020298e-08 \\ 
2 & 1 & 5 & 3 & 2.314798e+00 & 1.256411e-09 & 5.427736e-10 \\ 
\hline
2 & 2 & 1 & 3 & 5.133178e+00 & 3.150951e-08 & 6.138402e-09 \\ 
2 & 2 & 2 & 3 & 3.875948e+00 & 1.019905e-09 & 2.631369e-10 \\ 
2 & 2 & 3 & 3 & 3.677407e+00 & 3.374831e-11 & 9.177202e-12 \\ 
2 & 2 & 4 & 3 & 3.633887e+00 & 1.196563e-12 & 3.292791e-13 \\ 
2 & 2 & 5 & 3 & 1.100852e+00 & 1.071019e-14 & 9.729001e-15 \\ 
\hline
2 & 3 & 1 & 3 & 1.461766e+00 & 8.698889e-14 & 5.950944e-14 \\ 
2 & 3 & 2 & 3 & 1.118751e+00 & 4.096970e-15 & 3.662093e-15 \\ 
2 & 3 & 3 & 3 & 1.102424e+00 & 1.662951e-16 & 1.508449e-16 \\ 
2 & 3 & 4 & 3 & 3.178329e+00 & 1.221190e-16 & 3.842238e-17 \\ 
2 & 3 & 5 & 3 & 1.924223e+00 & 3.044738e-18 & 1.582320e-18 \\ 
\hline
3 & 1 & 1 & 3 & 5.278376e+00 & 5.346601e-04 & 1.012926e-04 \\ 
3 & 1 & 2 & 3 & 2.898394e+00 & 1.760686e-05 & 6.074697e-06 \\ 
3 & 1 & 3 & 3 & 2.480330e+00 & 4.867477e-07 & 1.962431e-07 \\ 
3 & 1 & 4 & 3 & 2.602304e+00 & 1.708061e-08 & 6.563648e-09 \\ 
3 & 1 & 5 & 3 & 2.594257e+00 & 5.017396e-10 & 1.934039e-10 \\ 
\hline
3 & 2 & 1 & 3 & 8.172169e+00 & 1.320095e-07 & 1.615355e-08 \\ 
3 & 2 & 2 & 3 & 4.770044e+00 & 3.005370e-09 & 6.300508e-10 \\ 
3 & 2 & 3 & 3 & 4.426838e+00 & 7.734334e-11 & 1.747146e-11 \\ 
3 & 2 & 4 & 3 & 4.521378e+00 & 1.996373e-12 & 4.415410e-13 \\ 
3 & 2 & 5 & 3 & 4.508090e+00 & 4.439516e-14 & 9.847886e-15 \\ 
\hline
3 & 3 & 1 & 3 & 5.015663e+00 & 9.627815e-12 & 1.919550e-12 \\ 
3 & 3 & 2 & 3 & 6.602139e+00 & 4.969235e-13 & 7.526705e-14 \\ 
3 & 3 & 3 & 3 & 6.132610e+00 & 1.126536e-14 & 1.836961e-15 \\ 
3 & 3 & 4 & 3 & 5.482751e+00 & 3.670736e-16 & 6.695062e-17 \\ 
3 & 3 & 5 & 3 & 5.346895e+00 & 4.774068e-17 & 8.928674e-18 \\ 
\hline
3 & 4 & 1 & 3 & 1.161979e+01 & 5.372252e-18 & 4.623365e-19 \\ 
3 & 4 & 2 & 3 & 4.069086e+00 & 1.622222e-17 & 3.986699e-18 \\
\hline
\end{tabular}
\end{center}
\label{tab::worst_merged_inv_conv}
\caption
    {
      We show the lowest value of
      $I$ for an entire Cartesian grid of size $32^D$.
      Volumes are  formed by a sphere (or circle in 2D) cutting the
      grid.   Small volumes here are merged with neighbors.
      We vary Taylor power $P^T$, weighting
      function exponents $P^W$, and dimensionality $D$. 
      Keep in mind
      that the effective condition number of the problem will be $(1/\sqrt(I))$.
    }
\end{table}

@@

We do also show that matrix conditioning is a  potential issue for
this class of algorihms.   In fact, for certain parameters,
the condition number  can be so severe that an
increase in matrix arithmetic precision will not be sufficient.
Since cell merger does not help the
problem, this lack of conditioning is not an issue with small cells.
With careful choices of polynomial order and weighting matrix, the
solvability problem can be managed, however.
